### 2024-07-27 conteudo/methods/methods.tex
Remove commentary about systematic fig, I do not want it anymore
remove commentary about add random selection algo, it is stupid

To make the random selection of function pairs, we list the code duplications for each of the 
X variations and execute a random selection algorithm built into the source code language of 
our tool. The exact algorithm of the random selection, with the selected function pairs, can 
be found in the Appendix (CREATE Appendix AND ADD HERE).

@@

The figure (CREATE FIGURE AND ADD HERE) illustrates the systematic approach described in this section.

>>>>

To make the random selection of function pairs, we list the code duplications for each of the 
X variations and execute a random selection algorithm built into the source code language of 
our tool. The random selected function selected function pairs can 
be found in the Appendix (CREATE Appendix AND ADD HERE).

@@
